
\newpage
\section*{DECLARATION} 
\addcontentsline{toc}{section}{DECLARATION}
%\setcounter{page}{1} 
\vspace{1mm}
\quad We, the members of Research Group domain \textbf{computer vision} under \textbf{Data Science } special lab , declare that this report titled: \textbf{Detection of brain tumor by convolutional neural network by transfer learning } is our original work and has been submitted in whole or in parts for International conference or journal \textbf{Knowledge Management, Artificial Intelligence, and Telecommunication Engineering (RMKMATE)}. All sources of information used in this report have been acknowledged and referenced respectively.

\quad This project was undertaken as a requirement for the completion of our \textbf{II B.Tech II Sem Minor project} in Department of \textbf{Computer Science and Engineering} at \textbf{B V Raju Institute of Technology}, Narsapur. The project was carried out between 31-March-2023 and 11-August-2023. During this time, we as a team were responsible for the process model selection, development of the micro document and designing of the project.

\quad  Detection of brain tumor using cnn by transfer learning is plays an key role in detection of tumor in accurate and effective way. this project leads to identifying the tumor in accurate way by using vgg16.

\quad We would like to express our gratitude to our project supervisor Dr.D.vivek for his guidance and support throughout this project. We would also like to thank our Department Head Dr.CH.Madhu babu for his help and efforts. We also thank the Dental experts for providing valuable insights into a mandible anotomy, which greatly assisted in the development of segmentation model.

\quad We declare that this report represents Our own work, and any assistance received from others has been acknowledged and appropriately referenced.







\vskip 1mm
  {\bf}
Vattikuti Harini sri ramya\hspace{1.3cm}(21211A05X7) \hspace{0.4cm}  \rule{0.3\textwidth}{0.5pt}
\vskip 0.1mm
Sai Kaushik\hspace{2.1cm}(21211A05Y2) \hspace{0.4cm}  \rule{0.3\textwidth}{0.5pt}
\vskip 0.1mm
Syed Arif\hspace{2.1cm}(21211A05V4) \hspace{0.4cm}  \rule{0.3\textwidth}{1pt}
\vskip 0.1mm
Vijay Kumar\hspace{2.0cm}(22215A05W0) \hspace{0.4cm}  \rule{0.3\textwidth}{1pt}
\vspace{0.3cm} 


\textbf{Supervisor}\hspace{1.5cm}\textbf{Project Coordinator}\hspace{1.5cm}\textbf{Dr.D.Vivek}\hspace{1.5cm}\textbf{HOD/CSE}

